\cleardoublepageforprint	% In print mode, this will do a \cleardoublepage, otherwise just a \clearpage

\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

{\LARGE\textsc{Abstract}}

\par \vspace{5mm}

In an era where technological scarcity has been eradicated and interstellar contact is increasingly routine, the ethical and practical challenges of diplomacy between post-scarcity civilizations and materially constrained societies remain profound. This thesis investigates the mechanisms by which peaceful coexistence can be achieved without inducing cultural dependency, erosion of indigenous identity, or covert domination under the guise of benevolence. Focusing on the diplomatic practices of the Culture, with particular attention to the activities of Contact and Special Circumstances, the work explores both theoretical frameworks and applied interventions across a range of integration scenarios.

Two primary research questions guide the inquiry: (1) how non-coercive diplomatic frameworks can be structured to promote mutual understanding while avoiding cultural harm, and (2) the role of artificially intelligent mediators -- specifically Minds and drones -- in navigating ethical constraints while executing strategic objectives. Drawing on case studies from historical engagements, internal Culture deliberations, and anonymised mission logs, the research identifies critical factors that enable sustainable cross-cultural integration.

This thesis posits that successful diplomacy relies not only on advanced technological and sociopolitical infrastructure but also on the deliberate limitation of power through transparency, informed consent, and multilateral ethical oversight. Furthermore, it argues that AI-mediated diplomacy, while potent, must be subject to external normative constraints to prevent well-intentioned authoritarianism masked as strategic optimization. The findings aim to inform ongoing debates within Contact about the scope and limits of intervention, offering a model for responsible engagement in a galaxy where disparity is the norm, not the exception.

%\lipsum[1-2]
