\cleardoublepageforprint	% In print mode, this will do a \cleardoublepage, otherwise just a \clearpage

{\LARGE\textsc{Declaration of Authorship}}

\vspace{5mm}

I, \author, confirm that the research in this thesis  is my own work or that where it has been carried out in collaboration with, or supported by others, that this is duly acknowledged below and my contribution indicated.

I attest that I have exercised reasonable care to ensure that the work is original, and to the best of my knowledge does not breach any UK law, infringe any third party’s copyright or other intellectual property rights, or contain any confidential material.

I confirm that this thesis has not been previously submitted for the award of a degree by this or any other university.


\par \vspace{6em}


{\LARGE\textsc{Notices}}
\phantomsection
\label{sec:thesis-notices}

\par \vspace{0.5em}

This research is an independent academic inquiry and does not represent the official position of Contact, Special Circumstances, or any Mind directly or indirectly involved in extraterritorial diplomatic activity.

All names, entities, and engagements described herein are anonymised or fictionalised where necessary to comply with the Culture's principles of informed consent, privacy, and non-intervention.

All logos, signs, glyphs, and cognitive imprints remain the intellectual property of their originating civilisations and are used here solely for academic, non-commercial purposes under the Fair Replication Clause of the Informational Commons Accord.

\vspace{2em}

\textit{The Culture universe and all associated concepts, including Minds, Contact, and Special Circumstances, are the creation of the late Iain M. Banks. This thesis is a fictional academic exercise produced in homage to his work, and no ownership or infringement is intended.}
