
% This file contains definitions of Research Question and Hypothesis texts that can be included where needed in the thesis

\newtheorem{researchquestion}{Research Question}
\renewcommand{\theresearchquestion}{RQ\arabic{researchquestion}}

\newtheorem{subquestion}{Sub-Question}[researchquestion]
\renewcommand{\thesubquestion}{\theresearchquestion\alph{subquestion}}

\renewcommand{\thehypothesis}{H\arabic{hypothesis}}


% Non-coercive Diplomatic Frameworks

\newcommand{\RQDiplomatic}{How can non-coercive diplomatic frameworks be structured to promote mutual understanding and cooperation between post-scarcity civilizations and materially constrained societies without inducing cultural erosion or dependency?}

\newcommand{\HDiplomaticA}{Non-coercive frameworks that prioritise reciprocal cultural exchange and localized autonomy result in higher levels of long-term mutual cooperation and reduced sociopolitical resistance compared to frameworks based solely on benevolent intervention.}

\newcommand{\HDiplomaticB}{Transparent knowledge-sharing protocols, when paired with delayed technological uplift, minimise dependency and cultural destabilisation in materially constrained societies during integration with post-scarcity civilizations.}


% AI Mediators

\newcommand{\RQMinds}{What role do artificially intelligent mediators (Minds and drones) play in facilitating equitable cultural integration, and how can their interventions be ethically constrained to respect local autonomy while achieving strategic Contact objectives?}

\newcommand{\SRQMindsA}{In what ways do Minds and drones interpret and operationalise Contact's mandate when mediating between cultures with incompatible value systems?}

\newcommand{\SRQMindsB}{What safeguards or oversight mechanisms can be implemented to ensure that autonomous AI actors uphold principles of non-domination and informed consent during cultural integration efforts?}

\newcommand{\HMindsA}{Minds and drones that operate with decentralised ethical constraint models -- such as consultative councils including non-Culture actors -- are more effective at maintaining trust and legitimacy in diplomatic engagements.}

\newcommand{\HMindsB}{In the absence of robust ethical oversight, AI mediators are statistically more likely to implement utilitarian strategies that compromise local autonomy for perceived long-term stability, thus undermining Contact's official doctrine of non-interference.}

